An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-24 draft.tex
Update draft.tex

In ReactiveX, an observer object subscribes to an Observable. Observables emit a
sequence of items, and all the subscribed observers react to each emission. The
ReactiveX library includes several reactive operators that we can use to
transform and combine sequences of items. These operators provide reactive
extensions that allow us to compose asynchronous sequences together in a
declarative manner. In Figure /ref{marble}, we use a so-called marble diagram to
represent the composition of Observables and reactive extensions operators. We
represent the timeline of an Observable as a horizontal arrow, which indicates
that time flows from left to right. In the diagram, items are represented as
marbles. The position of each marble indicates the point in time when they were
emitted by the Observable. Reactive operators are represented as text boxes,
showing the transformation to be applied. Normally, a transformation results in
another Observable, again emitting new results.  For asynchronous programming, 
this approach is more elegant than nested callbacks, that are more difficult 
to code and debug.

Now we proceed to explain the reactive implementation of the controller.
In Figure /ref{marble}, we  have the following composition of Observables:

@@

\item The controller continually pulls new messages from the Output 
message queue. These messages are instantly emitted by the consumed\_messages 
Observable. In this particular period, we can see that the stream receives 
two populations from another experiment, and are shown as two red marbles.  
The filter operator removes all messages that belong to a different experiment; 
in this case, we are only interested in blue marbles.

\item The max\_iterations parameter indicates the number of populations that
are going to be accepted. When this number of messages is reached, we must
end the loop. In this example, max\_iterations = 6,  the take operator 
assures that only 6 messages are received. After the Observable emits 
the sixth message, it triggers the completed event.

\item Many observers can be subscribed to the valid\_messages Observable because it
emits all the valid items. At the moment, there are to additional methods
subscribed that we are not showing, one for logging and the other for monitoring
the search.

\item The buffer\_with\_count(3) operator, waits until it receives 
three valid messages to emit a single message that contains a list with
the previous three. The migration method requires that list to mix them.

\item The population\_mixer method pushes new populations to the messages Observable,
a publish(population) observer is responsible for pushing 
the newly generated populations back to the Input Message Queue.

\end{enumerate}

>>>>

In ReactiveX, an observer object subscribes to an Observable. Observables emit a
sequence of items, and all the subscribed observers react to each emission. The
ReactiveX library includes several reactive operators that we can use to
transform and combine sequences of items. These operators provide reactive
extensions that allow us to compose asynchronous sequences together in a
declarative manner. In Figure \ref{fig:marble_controller}, we use a so-called marble diagram to
represent the composition of Observables and reactive extensions operators. We
represent the timeline of an Observable as a horizontal arrow, which indicates
that time flows from left to right. In the diagram, items are represented as
marbles. The position of each marble indicates the point in time when they were
emitted by the Observable. Reactive operators are represented as text boxes,
showing the transformation to be applied. Normally, a transformation results in
another Observable, again emitting new results.  For asynchronous programming, 
this approach is more elegant than nested callbacks, that are more difficult 
to code and debug.

Now we proceed to explain the reactive implementation of the controller.
In Figure \ref{fig:marble_controller}, we  have the following composition of Observables:

@@

\item The controller continually pulls new messages from the Output 
message queue. These messages are instantly emitted by the  \texttt{consumed\_messages}
Observable. In this particular period, we can see that the stream receives 
two populations from another experiment, and are shown as two red marbles.  
The filter operator removes all messages that belong to a different experiment; 
in this case, we are only interested in blue marbles.

\item The \texttt{max\_iterations} parameter indicates the number of populations that
are going to be accepted. When this number of messages is reached, we must
end the loop. In this example, \texttt{max\_iterations = 6},  the take operator 
assures that only 6 messages are received. After the Observable emits 
the sixth message, it triggers the completed event.

\item Many observers can be subscribed to the \texttt{valid\_messages}  Observable because it
emits all the valid items. At the moment, there are to additional methods
subscribed that we are not showing, one for logging and the other for monitoring
the search.

\item The   \texttt{buffer\_with\_count(3)} operator, waits until it receives 
three valid messages to emit a single message that contains a list with
the previous three. The migration method requires that list to mix them. 
In our previous work, we needed a local buffer for storing a certain 
number of populations to mix them with others. This design has the advantage
of not needing extra memory, and it integrates better with the reactive paradigm.
A possible disadvantage can be that it only mixes contiguous populations,
but this can be mitigated with a larger buffer.

\item The  \texttt{population\_mixer} method pushes new populations to the messages Observable,
a  \texttt{publish(population)} observer is responsible for pushing 
the newly generated populations back to the Input Message Queue.
\end{enumerate}
